### 2020-03-15 README.Rmd
Fix CI for Github Actions (#44)

<!-- badges: start -->
[![Build Status](https://img.shields.io/travis/mlr-org/mlr3spatiotempcv/master?label=macOS&logo=travis&style=flat-square)](https://travis-ci.org/mlr-org/mlr3spatiotempcv)
[![CircleCI build status](https://circleci.com/gh/mlr-org/mlr3spatiotempcv.svg?style=svg)](https://circleci.com/gh/mlr-org/mlr3spatiotempcv)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3spatiotempcv)](https://cran.r-project.org/package=mlr3spatiotempcv)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotempcv/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotempcv?branch=master)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![R CMD Check via {tic}](https://img.shields.io/github/workflow/status/mlr-org/mlr3spatiotempcv/R%20CMD%20Check%20via%20%7Btic%7D?logo=github&label=R%20CMD%20Check%20via%20{tic}&style=flat-square)](https://github.com/mlr-org/mlr3spatiotempcv/actions)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3spatiotempcv)](https://cran.r-project.org/package=mlr3spatiotempcv)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotempcv/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotempcv?branch=master)
<!-- badges: end -->
